Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-03-13 Scripts/Initial_Analysis.Rmd
fic bugs

# Set paths depending on machine Beast (jepa88), "carmelia" or Hall1000
if(Sys.info()[7] == "jepa88"){
  data_path <- "Z:/DATA/DBEM/"
}
if(Sys.info()[7] == "carmelia"){
  data_path <- paste(here(),"/Temporal_Data/",sep = "")
}
if(Sys.info()[7] == "hall1000"){
  data_path <- "/Volumes/DATA/DBEM/"
}

@@

    D_Path <- paste(Path,"/mpa0F1ENS",ensamble_list[c],"/", #<- drobo path for 8.5
                    taxon_key,"/",taxon_key,data_type,yr,".txt",
                    sep="")

@@

# dbem_import(
#   taxon_key <- 600004,
#   iyr <- 1951,
#   fyr <- 1952,
#   data_type <- "Abd",
#   ensamble_list = c(102,103),
#   Path <- paste(data_path,"DBEM/",sep="")
# )

@@

@@

Spp_list <- read.csv(paste(data_path,"Species/Species_list.csv",sep="")) %>% clean_names()
iyr <- 1951
fyr <- 2099
data_type <- "Catch"
ensamble_list = seq(102,111,1)
Path <- paste(data_path,"DBEM/",sep="")
world_grid <- tibble(index = seq(1,259200,1))
Neighbours <- read_excel(paste(data_path,"Spatial/EEZ_Neighbour_List.xlsx",sep="")) %>% 
  clean_names()

@@

@@

suppressWarnings(
  r_proportion_change <- bind_rows(
    lapply(
      Spp_list, #c(600004,600005),
      EstPropChange,
      iyr <- iyr,
      fyr <- fyr,
      data_type <- "Abd",
      ensamble_list = ensamble_list,
      Path <- paste(data_path,"DBEM/",sep=""),
      Neighbours = Neighbours
    )
  )
)
```

>>>>

# Set paths depending on machine Beast (jepa88), "carmelia" or Hall1000
if(Sys.info()[7] == "jepa88"){
  data_path <- "Z:/DATA/DBEM/"
}
if(Sys.info()[7] == "carmelia"){
  data_path <- paste(here(),"/Temporal_Data/",sep = "")
}
if(Sys.info()[7] == "hall1000"){
  data_path <- "/Volumes/DATA/JULIANO_NEYMAR/TransEmergence/Data/"
}

@@

    D_Path <- paste(Path,"mpa0F1ENS",ensamble_list[c],"/", #<- drobo path for 8.5
                    taxon_key,"/",taxon_key,data_type,yr,".txt",
                    sep="")

@@

dbem_import(
#   taxon_key <- 600004,
#   iyr <- 1951,
#   fyr <- 1952,
#   data_type <- "Abd",
#   ensamble_list = c(102,103),
#   Path <- DBEM_path
# )

@@

  # Get model data from spps
  SppDist <- dbem_import(
    taxon_key = Spp,
    iyr <- iyr,
    fyr <- fyr,
    data_type <- data_type,
    ensamble_list = ensamble_list,
    Path <- Path
  )

@@

iyr <- 1951
fyr <- 1953
data_type <- "Catch"
ensamble_list = seq(102,103,1)
DBEM_path <- "/Volumes/DATA/DATA/DBEM/"
world_grid <- tibble(index = seq(1,259200,1))
Neighbours <- read_excel(paste(data_path,"Spatial/EEZ_Neighbour_List.xlsx",sep="")) %>% 
  clean_names()

@@

Spp_list <- unique(Transboundary_spp$taxon_key)

@@

suppressWarnings(
  r_proportion_change <- bind_rows(
    lapply(
      Spp_list[1:2], #c(600004,600005),
      EstPropChange,
      iyr <- iyr,
      fyr <- fyr,
      data_type <- "Catch",
      ensamble_list = ensamble_list,
      Path =DBEM_path,
      Neighbours = Neighbours
    )
  )
)
